\EVOSUITE at the SBST 2021 Tool Competition

### 2022-03-04 papers/sbst22/paper_sbst22.tex
Copy paper from last year

%--------1---------2---------3---------4---------5---------6---------7
%
% Competition paper
% SBST 2013
% Page limit: 4 pages
%

@@

\author{%
%
\IEEEauthorblockN{%
Sebastian Vogl\IEEEauthorrefmark{1}, 
Sebastian Schweikl\IEEEauthorrefmark{1},
Gordon Fraser\IEEEauthorrefmark{1}, 
Andrea Arcuri\IEEEauthorrefmark{2},
Jose Campos\IEEEauthorrefmark{3},
and Annibale Panichella\IEEEauthorrefmark{4}%
}
%
\IEEEauthorblockA{\IEEEauthorrefmark{1}University of Passau, Germany\\
\{sebastian.vogl,sebastian.schweikl,gordon.fraser\}@uni-passau.de}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Kristiania University College, Norway\\andrea.arcuri@kristiania.no}
\IEEEauthorblockA{\IEEEauthorrefmark{3}University of Lisbon, Portugal\\jcmcampos@fc.ul.pt}
\IEEEauthorblockA{\IEEEauthorrefmark{4}Delft University of Technology, Netherlands\\A.Panichella@tudelft.nl}%
}

@@

\EVOSUITE~\cite{FrA11c} uses evolutionary search to automatically generate test
suites for Java classes. It takes as input the name of a target class as well
as the classpath containing the compiled bytecode of the class as well as its
dependencies. A basic static analysis extracts information about the relevant
classes as well as their constructors, methods, and fields. The bytecode is
instrumented while classes are loaded, such that \EVOSUITE can produce
execution traces for test executions, and to avoid test flakiness by replacing
non-deterministic calls with deterministic, mocked versions. \EVOSUITE then
applies meta-heuristic search algorithms to automatically produce a set of JUnit
test cases aimed at maximising code coverage. 
%Besides the basic command line interface there are also plugins for popular development environments such as IntelliJ, Eclipse, or Maven~\cite{ICST16_Tool}.

Originally, \EVOSUITE was implemented to optimise entire test suites with
respect to their overall code coverage~\cite{GoA_TSE12}. The latest search algorithm, which is now used by default, is the \textit{Dynamic Many-Objective Sorting Algorithm} (DynaMOSA) search algorithm~\cite{dynamosa} which operates at the test case level. 
%
The genetic encoding of test cases in \EVOSUITE consists of variable-length sequences of Java statements (e.g., primitive statements as well as calls on constructors or methods). Standard evolutionary search operators (e.g., selection, crossover, mutation) are adapted for this representation. 
%
\EVOSUITE supports multiple different coverage criteria that can be optimised simultaneously. The core fitness functions in \EVOSUITE are based on traditional heuristics for code coverage, such as the branch distance and the approach level (see~\cite{GoA_TSE12} for more details). Further criteria include mutation testing~\cite{emse14_mutation} as well as other basic
criteria~\cite{rojas2015combining}.

To improve the readability of the generated tests, \EVOSUITE applies post-processing once the available search budget has been exhausted~\cite{FrA11c,FrA13a}. In particular, minimisation is used to remove redundant tests and statements, and a minimised set of assertions is added using mutation analysis~\cite{10.1109/TSE.2011.93}. Finally, \EVOSUITE compiles and executes each test individually to avoid compile errors (which may be the result of bugs in \EVOSUITE) or flakiness caused by non-determinism in the class under test.

@@

The most recent version of \EVOSUITE (1.1.0) was used in the competition. As of
this version the default search algorithm in \EVOSUITE is
DynaMOSA~\cite{dynamosa}. No new features were added in this version, but
support for Java 9+ was added, several bugs were fixed, and a major refactoring
was applied to improve the code quality with respect to the use of Java
generics internally. Several smaller bugfixes were applied in the run-up to the
competition, which are now included in the current development version on
GitHub.

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{CoverageBoxV}
	\caption{\label{fig:results}Coverage results achieved in the competition.}
\end{figure}

With an overall score of 292.05, \EVOSUITE achieved the highest score of all
tools in the competition. As described in the competition
report~\cite{SBST:2021}, the score is calculated on the subset of 25 classes
for which all tools produced tests in some of the runs.
Figure~\ref{fig:results} summarises the results of \EVOSUITE in terms of the
mean coverage for the 25 classes used in the competition. While the coverage
increased from the 30 seconds to the 120 seconds search budget (mean line
coverage of 65.7\% vs. 77.1\%, respectively), the additional run of 300 seconds
actually shows a slight decrease (mean line coverage of 73.9\%). The likely
reason for this result is that \EVOSUITE crashed more frequently when given
more time. For example, for 76 runs of \EVOSUITE on the 25 classes no test
cases were generated. In the majority of these cases we found that the JVM
process running \EVOSUITE on the competition machine crashed with an
\texttt{OutOfMemoryException}, which possibly could have been avoided with a
more generous allocation of memory.

@@

This paper reports on the participation of the \EVOSUITE test generation tool
in the 9th SBST Java Unit Testing Tool Contest. On average, \EVOSUITE achieved
71\% branch coverage, 77\% line coverage, and a mutation score of 53\%, using a
search budget of 120 seconds on the 25 classes considered for the competition.
Overall, this results in a score of 292.05, which is the highest score of all
tools in the competition.

@@

%\noindent
\textbf{Acknowledgments:} Many thanks to all the contributors to \EVOSUITE.
This project has been funded by the EPSRC project ``GREATEST'' (EP/N023978/2).

>>>>

%--------1---------2---------3---------4---------5---------6---------7

@@

\author{%
%
\IEEEauthorblockN{%
Sebastian Vogl\IEEEauthorrefmark{1}, 
Sebastian Schweikl\IEEEauthorrefmark{1},
Gordon Fraser\IEEEauthorrefmark{1}, 
Andrea Arcuri\IEEEauthorrefmark{2},
Jose Campos\IEEEauthorrefmark{3},
and Annibale Panichella\IEEEauthorrefmark{4}%
}
%
\IEEEauthorblockA{\IEEEauthorrefmark{1}University of Passau, Germany\\
\{sebastian.vogl,sebastian.schweikl,gordon.fraser\}@uni-passau.de}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Kristiania University College and Oslo Metropolitan University, Norway\\andrea.arcuri@kristiania.no}
\IEEEauthorblockA{\IEEEauthorrefmark{3}University of Lisbon, Portugal\\jcmcampos@fc.ul.pt}
\IEEEauthorblockA{\IEEEauthorrefmark{4}Delft University of Technology, Netherlands\\A.Panichella@tudelft.nl}%
}

@@

\EVOSUITE~\cite{FrA11c} uses evolutionary search to automatically generate test
suites for Java classes. It takes as input the name of a target class as well
as the classpath describing where the compiled bytecode of the class as well as
its dependencies are located. A basic static analysis extracts information
about the relevant classes as well as their constructors, methods, and fields.
The bytecode is instrumented while classes are loaded, such that \EVOSUITE can
produce execution traces for test executions, and to avoid test flakiness by
replacing non-deterministic calls with deterministic, mocked versions.
\EVOSUITE then applies meta-heuristic search algorithms to automatically
produce a set of JUnit test cases aimed at maximising code coverage.
%Besides the basic command line interface there are also plugins for popular development environments such as IntelliJ, Eclipse, or Maven~\cite{ICST16_Tool}.

Originally, \EVOSUITE was implemented to optimise entire test suites with
respect to their overall code coverage~\cite{GoA_TSE12}. The latest search algorithm, which is now used by default, is the \textit{Dynamic Many-Objective Sorting Algorithm} (DynaMOSA) search algorithm~\cite{dynamosa} which operates at the test case level. 
%
The genetic encoding of test cases in \EVOSUITE consists of variable-length sequences of Java statements (e.g., primitive statements as well as calls on constructors or methods). Standard evolutionary search operators (e.g., selection, crossover, mutation) are adapted for this representation. 
%
\EVOSUITE supports multiple different coverage criteria that can be optimised simultaneously. The core fitness functions in \EVOSUITE are based on traditional heuristics for code coverage, such as the branch distance and the approach level (see~\cite{GoA_TSE12} for more details). Further fitness functions are based on mutation testing~\cite{emse14_mutation} as well as other basic criteria~\cite{rojas2015combining}.

To improve the readability of the generated tests and to avoid test smells~\cite{panichella2020revisiting}, \EVOSUITE applies post-processing once the available search budget has been exhausted~\cite{FrA11c,FrA13a}. In particular, minimisation is used to remove redundant tests and statements, and a minimised set of assertions is added using mutation analysis~\cite{10.1109/TSE.2011.93}. Finally, \EVOSUITE compiles and executes each test individually to avoid compilation errors (which may be the result of bugs in \EVOSUITE) or flakiness caused by non-determinism in the class under test.

@@

The most recent version of \EVOSUITE (1.1.0) was used in the competition. As of
this version, the default search algorithm in \EVOSUITE is
DynaMOSA~\cite{dynamosa}. No new features were added in this version, but
support for Java 9+ was added, several bugs were fixed, and a major refactoring
was applied to improve the code quality with respect to the use of Java
generics internally. Several smaller bugfixes were applied in the run-up to the
competition, which are now included in the current development version on
GitHub.

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{CoverageBoxV}
	\vspace{-2em}
	\caption{\label{fig:results}Coverage results achieved in the competition.}
	\vspace{-1em}
\end{figure}

With an overall score of 292.05, \EVOSUITE achieved the highest score of all
tools in the competition. As described in the competition
report~\cite{SBST:2021}, the score is calculated on the subset of 25 classes
for which all tools produced tests in some of the runs.
Figure~\ref{fig:results} summarises the results of \EVOSUITE in terms of the
mean coverage for the 25 classes used in the competition. While the coverage
increased from the 30 seconds to the 120 seconds search budget (mean line
coverage of 65.7\% vs. 77.1\%, respectively), the additional run of 300 seconds
actually shows a slight decrease (mean line coverage of 73.9\%). The likely
reason for this result is that \EVOSUITE crashed more frequently when given
more time. For example, for 76 runs of \EVOSUITE on the 25 classes no test
cases were generated. In most cases we found that the JVM process running
\EVOSUITE on the competition machine crashed with an
\texttt{OutOfMemoryException}, which possibly could have been avoided with a
more generous allocation of memory.

@@

This paper reports on the participation of the \EVOSUITE test generation tool
in the ninth SBST Java Unit Testing Tool Contest. On average, \EVOSUITE achieved
71\% branch coverage, 77\% line coverage, and a mutation score of 53\%, using a
search budget of 120 seconds on the 25 classes considered for the competition.
Overall, this results in a score of 292.05, which is the highest score of all
tools in the competition.

@@

%\noindent
\textbf{Acknowledgments:} Many thanks to all the contributors to
\EVOSUITE.
This project has been supported by EPSRC project % ``GREATEST'' 
EP/N023978/2.
